---
title: "Median house prices vs. income"
output: html_document
---

```{r}
#| message: false
#| echo: false
library(tidyverse, quietly = TRUE)
library(scales)
```

# Meet your neighbor (2 min)

Tell your neighbour your name, and something you've been enjoying this semester (academic or life).

# Load your sample

You will draw a random sample of 100 house blocks unique to you, based on your birthday.

In the code chunk below, enter your month, day and year of birth. If you were born on Jan 2, 2005 enter: mm = 1, dd = 2, yy = 2005.

```{r load_data}

mm = "your month of birth"
dd = "your day of birth"
yy = "your year of birth"

set.seed(as.numeric(paste0(mm, dd, yy)))
sample_house_blocks <- read_csv("house_price_data.csv") |> 
  sample_n(100)

```

Next, run the following code to visualize the house blocks of your random sample.

```{r}
sample_house_blocks |> 
  ggplot() +
  aes(x = median_house_value, y = median_income) +
  geom_point() +
  labs(y = "median income", x = "median house value") +
  scale_y_continuous(labels = dollar_format(scale = .01, suffix = "K")) +
    scale_x_continuous(labels = dollar_format(scale = .001, suffix = "K"))

```

Briefly compare with your neighbor's observations. By looking at the plot, which one of you has more observations with a high median house value?

# Fit linear regression line

Run the following code to fit a linear regression line.

```{r pressure, echo=FALSE}
model_housing <- lm(median_income ~ median_house_value, 
                    data = sample_house_blocks)
model_housing$coefficients |> round(4)
```


Plot the linear regression line by running the following chunk. 

```{r}

sample_house_blocks |> 
  ggplot() +
  aes(y = median_income, x = median_house_value) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(y = "median income", x = "median house value") +
  scale_y_continuous(labels = dollar_format(scale = .01, suffix = "K")) +
    scale_x_continuous(labels = dollar_format(scale = .001, suffix = "K"))

```

# Confidence interval for beta 1

```{r}

beta_hat_1 =  model_housing$coefficients[2]
t_cutoff = qt(0.975, df = nrow(sample_house_blocks) - 2)

se = summary(model_housing)$coefficients[2,]["Std. Error"]

ci_low <- (beta_hat_1 - t_cutoff * se) |> round(4)
ci_high <- (beta_hat_1 + t_cutoff * se) |> round(4)

print(paste("Lower bound is", ci_low))
print(paste("Upper bound is", ci_high))
```

Add your confidence interval lower and upper bounds to the next available line in this spreadsheet: bit.ly/owls-confidence


